\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

This dissertation presents the design, implementation, and evaluation
of a full-stack web platform that generates personalised programming
quizzes and coding challenges on demand using large language model
generation. The system addresses a limitation in existing technical education tools: existing platforms either offer static question banks that
grow stale, or expose raw AI-generated content without structure,
difficulty signals, or topic labels. The platform developed here
bridges that gap by combining the generative capability of large
language models with two custom-trained machine learning classifiers
that automatically enrich every generated question with a predicted
algorithmic topic tag and a predicted difficulty level, without
requiring a second model call or any manual curation.

The topic tag classifier was trained on a corpus of LeetCode
programming problems using a stochastic gradient descent estimator
over a combined word-level and character-level TF-IDF feature
representation. It achieved a test set accuracy of 0.805 and an
F1 macro score of 0.622 across ten algorithmic topic classes.
The difficulty classifier was trained on IBM Project CodeNet,
a dataset of over fourteen million competitive programming
submissions, using an XGBoost ensemble over engineered features
derived from submission statistics and problem description text.
Difficulty labels were derived from acceptance rate percentile
binning in the absence of explicit human annotations, and the
final model achieved a test set accuracy of 0.593 on a balanced
three-class problem. Both classifiers are deployed as in-process
singletons within a Python FastAPI backend, adding negligible
inference latency per generated question.

The platform additionally includes a sandboxed multi-language code
execution engine supporting Python, JavaScript, TypeScript, Java,
and C\#, a Monaco Editor coding environment, a JWT-authenticated
user account system with an experience point and levelling
mechanic, and a social friends network. The full system is
containerised using Docker Compose and deployable with a single
command. All six project objectives were met and evaluated against
measurable criteria on held-out test sets.